---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit this file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# ChromoCorrect

<!-- badges: start -->
<!-- badges: end -->

ChromoCorrect is an R Package and R Shiny app that detects and corrects for chromosomal location bias in read counts.

## Installation

You can install the development version of ChromoCorrect from [GitHub](https://github.com/) in R with:

``` r
# install.packages("devtools")
devtools::install_github("gerisullivan/ChromoCorrect")
```
## Dependencies

### RTools
Some packages rely on R packages from source which requires RTools to download. 
Windows: download RTools from https://cran.r-project.org/bin/windows/Rtools/
MacOS: the Xcode suite (if not already installed) is available at https://developer.apple.com/xcode/resources/

## Bioconductor
There are some R packages required to be installed from Bioconductor. If they do not download as dependencies when installing ChromoCorrect, you can install them yourself below:

```{r}
if (!require("BiocManager", quietly = TRUE))
    install.packages("BiocManager")
BiocManager::install("FBN", "locfit", "edgeR", "limma")
```


## Example - running the app

To start the shiny app:

```{r eval=FALSE}
library(ChromoCorrect)
launch_app()
```

## Further instructions

Please see the [Instructions](/inst/Instructions.html) file for detailed information on running the ChromoCorrect app or the commands independently of the app.
